The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
fig 5 caption

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, forage, and open) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
varied for winter layers becoming relatively stable at 200 observations and
remained weak throughout for summer layers. B) Mean layer relevance across
individuals increased for winter layers and slightly increased for summer
layers. C) Similarity of landcover network layers between seasons (e.g. open
summer compared to open winter) showed a stabilizing layer similarity at 200
observations for forest and 300 observations for lichen and open. 
<!--TODO:*There were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.* **Brief explanation of why two landcover don't
have values at lower nobs??**.--> D) Mean connective redundancy across
individuals increased with increasing number of observations, which begins to
plateau around 100 observations. Note, data in panel C are truncated because 
there were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.

>>>>

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, forage, and open) across two seasons (summer and
winter) and four network metrics calculated. A) Mean graph strength across
individuals varied for winter layers becoming relatively stable at 200
observations and remained weak throughout for summer layers. B) Mean layer
relevance across individuals increased for winter layers and slightly increased
for summer layers. C) Similarity of landcover network layers between seasons
(e.g. open summer compared to open winter) showed a stabilizing layer similarity
at 200 observations for forest and 300 observations for lichen and open.
<!--TODO:*There were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.* **Brief explanation of why two landcover don't
have values at lower nobs??**.--> D) Mean connective redundancy across
individuals increased with increasing number of observations, which begins to
plateau around 100 observations. Note, data in panel C are truncated because
there were few observations of individuals in foraging and open habitats during
the winter, resulting in inability to calculate layer similarity at lower number
of observations.
